Computing Entropies With Nested Sampling

### 2017-03-10 paper/ms.tex
slight tweaks

% Full title of the paper (Capitalized)
\Title{Calculating Entropies With Nested Sampling}

@@

The entropy quantifies the degree to which the issue
``what is the value of $x$, precisely?'' remains unresolved. For example,
if there is only one possible value which has probability 1, $H_x$ is
zero\footnote{Conventionally, $0 \times \log 0$ is defined to be equal
to $\lim_{x \to 0^+} x\log x$, which is zero.}.
If there are $N$ possibilities with equal probabilities $1/N$ each,
then the entropy is $H_x = \log(N)$.

@@

Throughout this paper, I use the compact
`overloaded' notation for probability distributions, writing $p(x)$ instead
of the more cumbersome $P(X=x)$.
Probability distribution is implicitly conditional on some prior
information, which has been omitted from the notation unless necessary.
All logarithms are written $\log$ and any base can be used, unless otherwise
specified (for example by writing $\ln$ or $\log_{10}$). Any numerical
values given for the value of specific entropies are in {\em nats}, i.e.,
the natural logarithm was used.

@@

The entropy of the prior $p(\x)$ describes the degree to which the question
``what is the value of $\x$, precisely?'', while the
entropy of the joint prior $p(\x, \d)$
describes the degree to which the question
``what is the value of the pair $(\x, \d)$, precisely?'' remains unanswered.

>>>>

% Full title of the paper (Capitalized)
\Title{Computing Entropies With Nested Sampling}

@@

The entropy quantifies the degree to which the issue
``what is the value of $x$, precisely?'' remains unresolved. For example,
if there is only one possible value which has probability 1, $H_x$ is
zero\footnote{Conventionally, $0 \times \log 0$ is defined to be equal
to $\lim_{x \to 0^+} (x\log x)$, which is zero.}.
If there are $N$ possibilities with equal probabilities $1/N$ each,
then the entropy is $H_x = \log(N)$.

@@

Throughout this paper, I use the compact
`overloaded' notation for probability distributions, writing $p(x)$ instead
of the more cumbersome $P(X=x)$.
Probability distributions are implicitly conditional on some prior
information, which is omitted from the notation unless necessary.
All logarithms are written $\log$ and any base can be used, unless otherwise
specified (for example by writing $\ln$ or $\log_{10}$). Any numerical
values given for the value of specific entropies are in {\em nats}, i.e.,
the natural logarithm was used.

@@

The entropy of the prior $p(\x)$ describes the degree to which the question
``what is the value of $\x$, precisely?'' remains unanswered, while the
entropy of the joint prior $p(\x, \d)$
describes the degree to which the question
``what is the value of the pair $(\x, \d)$, precisely?'' remains unanswered.
